Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2021-12-10 Manuscript/FLPhish(Trans).tex
更新： 修改abstract和conclusion的语法错误 notation把matrix放在后面 cite错误更改

\begin{table}[t]
  \caption{Summary of Notations}
  \resizebox{0.5\textwidth}{!}{
  \begin{tabular}{lp{6cm}}
    \bottomrule
    Term&Description\\
    \hline
    $s$ & central server in FL \\
    $\mathbf{M}$ & global model preserved by $s$\\
    $c_i$ & the $i$th client in FL, $i=1,2,3,...,u$ \\
    $d_i$ & the local dataset preserved by the $i$th client \\
    $C$ & the ensemble of all the clients \\
    $u$ & the number of clients\\
    $\mathbf{m_i}$ & local models trained by the $i$th client\\
    $D_t$ & the unlabeled dataset chosen by $s$ in each procedure\\
    $D$ & the unlabeled dataset preserved by $s$\\
    $n$ & the number of samples in $D_t$\\
    $B_t$ & the labeled dataset (\textit{`bait'}) chosen by $s$ in each procedure\\
    $B$ & the labeled dataset preserved by $s$\\
    $m$ & the number of samples in $B_t$\\
    $\mathbf{k_i^t}$ & the predictions (\textit{`knowledge'}) made by the $i$th client in the $t$th procedure\\
    $a_i^t$ & the accuracy of predictions of $B_t$ made by $c_i$ in $t$th procedure\\
    $q_i$ & the label of $c_i$ to judge it is a malicious client or not\\
    $r_q$ & the threhold of malicious clients\\
    $x^t_l$ & the $l$th data point in $D_t$\\
    $\mathbf{\hat{y}^t_l}$ & the ensembled prediction of data point $x^t_l$\\
    $\mathbf{\hat{y}^i_l}$ & the prediction of $l$th data point made by $i$th client\\
    $\mathbf{K_t}$ & the aggregated labels (predictions) of the $t$th round's unlabeled dataset\\
    \hline
  \end{tabular}
  }
\end{table}

\section{Introduction}
\IEEEPARstart{M}{any} elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection. To learn complex rules, such activities necessitate a large dataset. In most cases, these huge datasets are gathered from users, such as the app's users. Developers get information from users and utilize it to create the dataset. Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy protection, making it difficult to get data directly from consumers any more. Under these circumstances, each individual's data is referred to as an `Isolated Data Island'. The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_02_FLConcept}. FL is a privacy-preserving machine learning solution that allows a central server to train a global model without gaining access to individuals' personal privacy data. Instead of training global model on users' private data, the central server in FL just needs to train its global model using their gradient updates. FL protects an individual's privacy while simultaneously reducing the load on the central server by leveraging the capabilities of distributed computation and storage. FL is soon applied by many companies. Google built the world's first product-level scalable mobile FL system based on TensorFlow\footnote{https://federated.withgoogle.com/}. Its FL system could be operated on thousands of mobile phones. Moreover, a team of WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction. And some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp}.

@@

\par Former researchers have offered certain Byzantine-robust techniques to deal with malevolent Byzantine clients in FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. In the presence of a bounded number of malicious clients, Byzantine-robust approaches try to develop a global model with high accuracy. According to their different mechanisms, we divide Byzantine-robust approaches into two major kinds. The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients. The server then eliminates the suspected clients' gradient updates from the aggregate process. For instance, in DRACO, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another group of Byzantine-robust approaches (dubbed Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}. The FL server sorts the values of each parameter based on Median and selects the median value of each parameter as the value to be used in global model updates. Recent research, however, suggest that current approaches are still vulnerable to Byzantine attacks \cite{ref_06_model}. We present a novel reputation-based phishing scheme (called FLPhish) in defending against Byzantine attacks in Ensemble FL. Our contributions are four-folds:
\begin{itemize}
  \item First, we design a new FL architecture, Ensemble Federated Learning (called Ensemble FL). Ensemble FL utilizes an unlabeled dataset to replace the gradient updates in traditional FL. This architecture supports different types of deep learning models in each client and makes FL more flexible.
  \item Second, we craft a `phishing' method based on Ensemble FL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system. It preserves the security of Ensemble FL.
  \item Third, we present a bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients. The reputation mechanism helps FLPhish identify the Byzantine clients more accurately.
  \item Last, we propose two aggregation algorithms FLPhish-threshold and FLPhish-weight to aggregate the predictions of the FL clients, based on reputation mechanism. FLPhish using FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish with FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate aggregation process. These two algorithms contribute to the robustness of FLPhish.
\end{itemize}

@@

\subsection{Byzantine Defense Methods in Federated Learning}
Recent years have witnessed the increasing interest in the research of Byzantine-robust schemes in the context of FL. Most of the current Byzantine-robust FL methods tend to make a more robust aggregation rule which aims to tolerate the presence of Byzantine clients. 
For example, in 2017, Chen \textit{et al}. Krum developed an approach \cite{ref_12_defense}. Krum selects one client's update as a global model based on a square-distance score in each iteration. 
In the same year, Blanchard \textit{et al}. proposed two Byzantine-tolerant FL aggregation algorithms Trimmed mean and Median \cite{ref_16_defense}. Trimmed Mean considers each parameter of the model update individually. Trimmed Mean sorts the parameter of the model updates collected. Median sorts the values of each parameter of all local model updates as well. And it considers the median value of each parameter as the value of the parameter in the global model update. 
In 2018, Chen \textit{et al.} designed an approach Draco to evaluate redundant gradients that are used by the parameter server to eliminate the effects of adversarial updates. 
In 2019, Zeno uses a ranking-based preference mechanism \cite{ref_15_defense}. The server computes a score for each client by using the stochastic zero-order oracle. Then Zeno presents a ranking list of clients based on the estimated descent of the loss function and the magnitudes. At last, Zeno computes the global model update by aggregating the clients with the highest scores. 
In 2020, SLSGD developed by Xie \textit{et al.} also uses trimmed mean as the robust aggregation rules for Byzantine-robust FL \cite{ref_14_defense}. 
In the same year, Cao \textit{et al.} proposed a Byzantine-tolerant scheme: FLTrust to introduce the use of trust \cite{ref_17_defense}. In each iteration, the server calculates a trust score for each client at first, and lowers the trust score if the client's local model update's direction deviates more from the direction of the global model update. The client with a trust score lower than the threshold is considered a malicious client.
In 2021, a privacy-enhanced FL (PEFL) framework is presented by Liu \textit{et al.}  \cite{ref_45_defense}. PEFL takes advantages of homomorphic encryption to protect the privacy of the clients. Furthermore, a channel using the effective gradient data extraction is provided for the server to punish poisoners.

\subsection{Reputation Mechanism in Information Security}
The reputation mechanism is valued as a way to measure an entity's performance in a long term, such as in an online social network \cite{ref_27_reputation}, and in a smart grid system \cite{ref_41_reputation, ref_44_reputation}.
In 2012, Das \textit{et al.} first presented a dynamic trust computation model called SecuredTrust. This framework is used to distribute the workload and deal with the altering behavior of malicious clients \cite{ref_48_reputation}.
In 2015, Zhu \textit{et al.} proposed an authenticated trust and reputation calculation and management system in wireless sensor network and cloud computing to calculate and manage trust and reputation of the service of CSP and SNP \cite{ref_47_reputation}.
In 2018, Lei \textit{et al.} presented a Reputation-based Byzantine Fault Tolerance algorithm that incorporates a reputation model to evaluate the performance of each node in the blockchain system \cite{ref_25_reputation}. The nodes get lower discourse rights and reputation in the voting process if any malicious behavior is detected by the system. Furthermore, they presented a reputation-based primary change scheme. The node with a higher reputation would get greater opportunities to generate new valid blocks, which reduces the security risk of the system.
In 2020, Chouikhi \textit{et al.} built a model for reputation computing and a credibility model to enhance network efficiency \cite{ref_23_reputation}. They used the reputation score or value to measure the behavior of a vehicle towards other vehicles and network services. And the credibility of vehicles is used to determine the accuracy of a reputation score offered by a vehicle. 
In the same year, Wen \textit{et al.} proposed a Dirichlet reputation-based scheme and adopt the reputation score to select a trustworthy Helper as a friendly jammer in a wireless cooperative system (WCS) \cite{ref_24_reputation}. Furthermore, they developed an artificial noise detection method with multiple thresholds. They provided ratings with multiple graded levels. In the Dirichlet reputation-based scheme, the graded ratings were directly expressed and reflected in the derived reputation scores.
In 2021, Liang \textit{et al.} presented a markov-based reputation scheme in an intrusion detection system. The Hidden Generalized Mixture Transition Distribution (HgMTD) model, namely RS-HgMTD, is developed to assist each vehicle in the VANET to measure the creditworthiness of its neighbor vehicles \cite{ref_46_reputation}.

@@

\subsection{Threat Model}
However, the current system still suffers from multiple problems, especially Byzantine attacks. Malicious Byzantine client $b$ initiates untargeted Byzantine attacks towards the global model via the label flipping attack in the current system model. Label-flipping requires $b$ to modify the labels of training data and ensure the features of data unchanging \cite{ref_18_label_flipping}. Byzantine client $b$'s local model is trained with false labels, thus constructing a `poisoned' model with low accuracy. Then Byzantine client $b$ dispatches the false updates of the gradient to the central server. Therefore the false updates of the gradient cause the central server to learn false distilled knowledge from clients. The server $s$'s aggregation process is played on FedAvg which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$. This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight. Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $c_{i}$ can declare a fake size number larger than $d_{i}$'s real size number. If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions.

@@

\begin{figure*}[!htp]
  \centering
    \subfigure[$q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_1.pdf}}
    \subfigure[$q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_2.pdf}}
    \subfigure[$q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_5.pdf}}
    \subfigure[$q=0.9$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_9.pdf}}
  \\
  \caption{Reputation values of experiments on MNIST on different imbalance degrees.}
  \label{fig_exp_mnist-reputation}
  \vspace{0.2in}
\end{figure*}

\begin{figure*}[!htp]
  \centering
    \subfigure[$q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_1.pdf}}
    \subfigure[$q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_2.pdf}}
    \subfigure[$q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_5.pdf}}
    \subfigure[$q=0.9$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_9.pdf}}
  \\
  \caption{Reputation values of experiments on Fashion-MNIST on different imbalance degrees.}
  \label{fig_exp_fashion_reputation}
  \vspace{0.2in}
\end{figure*}

\begin{figure*}[!htp]
  \centering
    \subfigure[{$q=$}0.1]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_1.pdf}}
    \subfigure[{$q=$}0.2]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_2.pdf}}
    \subfigure[{$q=$}0.5]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_5.pdf}}
    \subfigure[{$q=$}0.9]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_9.pdf}}
  \\
  \caption{Reputation values of experiments on CIFAR-10 on different imbalance degrees.}
  \label{fig_exp_cifar_reputation}
  \vspace{0.2in}
\end{figure*}

@@

  \subsection{Performance Comparison under Random Attacks}
    From Fig. \ref{fig_exp_extreme}, Fig. \ref{fig_table_mnist_random}, Fig. \ref{fig_table_fashion_random} and Fig. \ref{fig_table_cifar_random} , we can see that random Byzantine attacks have poor performance against FLPhish-weight and FLPhish-threshold (threshold=0.1, 0.2). We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point like untargeted Byzantine attackers do. While we can see that it has good results in attacking FLPhish-threshold(threshold=0.5) in the CIFAR-10 dataset. From Fig. \ref{fig_exp_cifar_reputation}, we can see that the reputation of benign clients in CIFAR-10 experiments rapidly falls under the threshold of 0.5 due to the complexity of the tasks. With the increase of imbalance degree value $q$, the reputation of the benign clients falls more rapidly in the experiments of the CIFAR-10 dataset than in the experiments of the MNIST and the Fashion-MNIST dataset. As benign clients' reputations in the experiments of the CIFAR-10 dataset become under the threshold $\tau$ of 0.5, they are identified as malicious Byzantine clients as well. As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assit the aggregation, therefore causing a bad performance of FLPhish-threshold (threshold=0.5). While, we can see that FLPhish-threshold (threshold=0.1), FLPhish-threshold (threshold=0.2) and FLPhish-weight stood still against the random Byzantine attacks. The results indicate that the value of the threshold $\tau$ should be considered carefully in the application in some complex tasks.

@@

    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish-threshold and FLPhish-weight under the condition where Byzantine client portion is a fixed value 0.5 and distribution imbalance value $q$ is different across the Experiments. The experiment results are shown in Table \ref{table_exp_imbalances_untargeted}. From Table \ref{table_exp_imbalances_untargeted}, we can observe that both the FLPhish-threshold and FLPhish-weight outperform baseline until the imbalance degree $q$ reaches 0.8. The imbalance degree $q$ of 0.8 means that the distribution of data becomes extremely non-IID. The performance of FLPhish-threshold with a threshold of 0.5 rapidly falls in this case. When facing the distribution of imbalance degree $q=0.8$, each client performs badly, bringing a decline to its reputation. The rise of imbalance degree brings an explosive decline to the global model's accuracy. The accuracy of the global model under the FLPhish-threshold of threshold 0.5 stays 0.1 in the whole learning process. It means that the FLPhish-threshold of threshold 0.5 identifies all the clients as Byzantine clients, making the aggregation process invalid. We can see that the FLPhish-threshold of threshold 0.2 outperforms others. When the distribution becomes non-IID, the threshold of FLPhish-threshold should be set to a lower value to avoid a high false-negative rate. In the experiment of MNIST, it should be set to 0.2. Meanwhile, the performance of FLPhish-weight remain stable under different imbalance degrees.

@@

    \subsubsection{\ul{Performance Comparison with Different Fractions of Byzantine Clients}} Different fractions of Byzantine clients are taken into account as well. Table \ref{table_exp_byzantines_untargeted} shows that the accuracy for FedAvg and Ensemble FL without any defense mechanisms begins to fall rapidly when the Byzantine portion reaches nearly 50\%. Furthermore, FedAvg performs extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers. In comparison, FLPhish's (including FLPhish-threshold and FLPhish-weight) performance under various thresholds maintains a high level of performance as the portion grows. Both FLPhish-threshold and FLPhish-weight effectively detect Byzantine clients and accurately discards them from the aggregation process. The global model can be successfully trained without the involvement of Byzantine clients in aggregation procedures. Furthermore, the data show that FLPhish-threshold with a 0.1 threshold performs worse than the other two. This is due to the fact that the 0.1 threshold is far too low to adequately detect Byzantine clients. Though the Byzantine attackers will try to make right predictions of the public dataset and then send the opposite wrong predictions to the FL server. But they will also make wrong predictions first and coincidentally transfer the opposite right predictions to the FL server. Thus the reputation values of some Byzantine clients, in particular, can exceed 0.1. It indicates that if the threshold is not well set, Byzantine clients can avoid being detected by FLPhish-threshold. As the fractions of Byzantine clients go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks will increase rapidly for they outnumber the fractions of the benign clients. In the mean time, FLPhish-weight show stable performance whenever the fractions of Byzantine clients are.

>>>>

\begin{table}[t]
  \caption{Summary of Notations}
  \resizebox{0.5\textwidth}{!}{
  \begin{tabular}{lp{6cm}}
    \bottomrule
    Term&Description\\
    \hline
    $s$ & central server in FL \\
    $c_i$ & the $i$th client in FL, $i=1,2,3,...,u$ \\
    $d_i$ & the local dataset preserved by the $i$th client \\
    $C$ & the ensemble of all the clients \\
    $u$ & the number of clients\\
    $D_t$ & the unlabeled dataset chosen by $s$ in each procedure\\
    $D$ & the unlabeled dataset preserved by $s$\\
    $n$ & the number of samples in $D_t$\\
    $B_t$ & the labeled dataset (\textit{`bait'}) chosen by $s$ in each procedure\\
    $B$ & the labeled dataset preserved by $s$\\
    $m$ & the number of samples in $B_t$\\
    $a_i^t$ & the accuracy of predictions of $B_t$ made by $c_i$ in $t$th procedure\\
    $q_i$ & the label of $c_i$ to judge it is a malicious client or not\\
    $r_q$ & the threhold of malicious clients\\
    $x^t_l$ & the $l$th data point in $D_t$\\
    $\mathbf{M}$ & global model preserved by $s$\\
    $\mathbf{m_i}$ & local models trained by the $i$th client\\
    $\mathbf{k_i^t}$ & the predictions (\textit{`knowledge'}) made by the $i$th client in the $t$th procedure\\
    $\mathbf{\hat{y}^t_l}$ & the ensembled prediction of data point $x^t_l$\\
    $\mathbf{\hat{y}^i_l}$ & the prediction of $l$th data point made by $i$th client\\
    $\mathbf{K_t}$ & the aggregated labels (predictions) of the $t$th round's unlabeled dataset\\
    \hline
  \end{tabular}
  }
\end{table}

\section{Introduction}
\IEEEPARstart{M}{any} elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection. To learn complex rules, such activities necessitate a large dataset. In most cases, these huge datasets are gathered from users, such as the app's users. Developers get information from users and utilize it to create the dataset. Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy protection, making it difficult to get data directly from consumers anymore. Under these circumstances, each individual's data is referred to as an `Isolated Data Island'. The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_02_FLConcept}. FL is a privacy-preserving machine learning solution that allows a central server to train a global model without gaining access to individuals' private data. Instead of training the global model on users' private data, the central server in FL just needs to train its global model using their gradient updates. FL protects an individual's privacy while simultaneously reducing the load on the central server by leveraging the capabilities of distributed computation and storage. FL is soon applied by many companies. Google built the world's first product-level scalable mobile FL system based on TensorFlow\footnote{https://federated.withgoogle.com/}. Its FL system could be operated on thousands of mobile phones. Moreover, a team of WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction. And some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp}.

@@

\par Former researchers have offered certain Byzantine-robust techniques to deal with malevolent Byzantine clients in FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. In the presence of a bounded number of malicious clients, Byzantine-robust approaches try to develop a global model with high accuracy. According to their different mechanisms, we divide Byzantine-robust approaches into two major kinds. The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients. The server then eliminates the suspected clients' gradient updates from the aggregate process. For instance, in DRACO, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another group of Byzantine-robust approaches (dubbed Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}. The FL server sorts the values of each parameter based on Median and selects the median value of each parameter as the value to be used in global model updates. Recent research, however, suggests that current approaches are still vulnerable to Byzantine attacks \cite{ref_06_model}. We present a novel reputation-based phishing scheme (called FLPhish) in defending against Byzantine attacks in Ensemble FL. Our contributions are four-folds:
\begin{itemize}
  \item First, we design a new FL architecture, Ensemble Federated Learning (called Ensemble FL). Ensemble FL utilizes an unlabeled dataset to replace the gradient updates in traditional FL. This architecture supports different types of deep learning models in each client and makes FL more flexible.
  \item Second, we craft a `phishing' method based on Ensemble FL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system. It preserves the security of Ensemble FL.
  \item Third, we present a bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients. The reputation mechanism helps FLPhish identify the Byzantine clients more accurately.
  \item Last, we propose two aggregation algorithms FLPhish-threshold and FLPhish-weight to aggregate the predictions of the FL clients, based on reputation mechanism. FLPhish using FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish with FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate aggregation process. These two algorithms contribute to the robustness of FLPhish.
\end{itemize}

@@

\subsection{Byzantine Defense Methods in Federated Learning}
Recent years have witnessed the increasing interest in the research of Byzantine-robust schemes in the context of FL. Most of the current Byzantine-robust FL methods tend to make a more robust aggregation rule which aims to tolerate the presence of Byzantine clients. 
For example, in 2017, Chen \textit{et al}. Krum developed an approach \cite{ref_12_defense}. Krum selects one client's update as a global model based on a square-distance score in each iteration. 
In the same year, Blanchard \textit{et al}. proposed two Byzantine-tolerant FL aggregation algorithms Trimmed mean and Median \cite{ref_16_defense}. Trimmed Mean considers each parameter of the model update individually. Trimmed Mean sorts the parameter of the model updates collected. Median sorts the values of each parameter of all local model updates as well. And it considers the median value of each parameter as the value of the parameter in the global model update. 
In 2018, Chen \textit{et al.} designed an approach Draco to evaluate redundant gradients that are used by the parameter server to eliminate the effects of adversarial updates. 
In 2019, Zeno uses a ranking-based preference mechanism \cite{ref_15_defense}. The server computes a score for each client by using the stochastic zero-order oracle. Then Zeno presents a ranking list of clients based on the estimated descent of the loss function and the magnitudes. At last, Zeno computes the global model update by aggregating the clients with the highest scores. 
In 2020, SLSGD developed by Xie \textit{et al.} also uses trimmed mean as the robust aggregation rules for Byzantine-robust FL \cite{ref_14_defense}. 
In the same year, Cao \textit{et al.} proposed a Byzantine-tolerant scheme: FLTrust to introduce the use of trust \cite{ref_17_defense}. In each iteration, the server calculates a trust score for each client at first, and lowers the trust score if the client's local model update's direction deviates more from the direction of the global model update. The client with a trust score lower than the threshold is considered a malicious client.
In 2021, a privacy-enhanced FL (PEFL) framework is presented by Liu \textit{et al.}  \cite{ref_45_defense}. PEFL takes advantage of homomorphic encryption to protect the privacy of the clients. Furthermore, a channel using the effective gradient data extraction is provided for the server to punish poisoners.

\subsection{Reputation Mechanism in Information Security}
The reputation mechanism is valued as a way to measure an entity's performance in a long term, such as in an online social network \cite{ref_27_reputation}, and in a smart grid system \cite{ref_41_reputation, ref_44_reputation}.
In 2012, Das \textit{et al.} first presented a dynamic trust computation model called SecuredTrust. This framework is used to distribute the workload and deal with the altering behavior of malicious clients \cite{ref_48_reputation}.
In 2015, Zhu \textit{et al.} proposed an authenticated trust and reputation calculation and management system in wireless sensor network and cloud computing to calculate and manage trust and reputation of the service of CSP and SNP \cite{ref_47_reputation}.
In 2018, Lei \textit{et al.} presented a Reputation-based Byzantine Fault Tolerance algorithm that incorporates a reputation model to evaluate the performance of each node in the blockchain system \cite{ref_25_reputation}. The nodes get lower discourse rights and reputation in the voting process if any malicious behavior is detected by the system. Furthermore, they presented a reputation-based primary change scheme. The node with a higher reputation would get greater opportunities to generate new valid blocks, which reduces the security risk of the system.
In 2020, Chouikhi \textit{et al.} built a model for reputation computing and a credibility model to enhance network efficiency \cite{ref_23_reputation}. They used the reputation score or value to measure the behavior of a vehicle towards other vehicles and network services. And the credibility of vehicles is used to determine the accuracy of a reputation score offered by a vehicle. 
In the same year, Wen \textit{et al.} proposed a Dirichlet reputation-based scheme and adopt the reputation score to select a trustworthy Helper as a friendly jammer in a wireless cooperative system (WCS) \cite{ref_24_reputation}. Furthermore, they developed an artificial noise detection method with multiple thresholds. They provided ratings with multiple graded levels. In the Dirichlet reputation-based scheme, the graded ratings were directly expressed and reflected in the derived reputation scores.
In 2021, Liang \textit{et al.} presented a Markov-based reputation scheme in an intrusion detection system. The Hidden Generalized Mixture Transition Distribution (HgMTD) model, namely RS-HgMTD, is developed to assist each vehicle in the VANET to measure the creditworthiness of its neighbor vehicles \cite{ref_46_reputation}.

@@

\subsection{Threat Model}
However, the current system still suffers from multiple problems, especially Byzantine attacks. Malicious Byzantine client $b$ initiates untargeted Byzantine attacks towards the global model via the label flipping attack in the current system model. Label-flipping requires $b$ to modify the labels of training data and ensure the features of data are unchanging \cite{ref_18_label_flipping}. Byzantine client $b$'s local model is trained with false labels, thus constructing a `poisoned' model with low accuracy. Then Byzantine client $b$ dispatches the false updates of the gradient to the central server. Therefore the false updates of the gradient cause the central server to learn false distilled knowledge from clients. The server $s$'s aggregation process is played on FedAvg which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$. This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight. Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $c_{i}$ can declare a fake size number larger than $d_{i}$'s real size number. If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions.

@@

\begin{figure*}[!htp]
  \centering
    \subfigure[$q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_1.pdf}}
    \subfigure[$q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_2.pdf}}
    \subfigure[$q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_5.pdf}}
    \subfigure[$q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_9.pdf}}
  \\
  \caption{Reputation values of experiments on MNIST on different imbalance degrees.}
  \label{fig_exp_mnist-reputation}
  \vspace{0.2in}
\end{figure*}

\begin{figure*}[!htp]
  \centering
    \subfigure[$q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_1.pdf}}
    \subfigure[$q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_2.pdf}}
    \subfigure[$q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_5.pdf}}
    \subfigure[$q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_9.pdf}}
  \\
  \caption{Reputation values of experiments on Fashion-MNIST on different imbalance degrees.}
  \label{fig_exp_fashion_reputation}
  \vspace{0.2in}
\end{figure*}

\begin{figure*}[!htp]
  \centering
    \subfigure[{$q=$}0.1]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_1.pdf}}
    \subfigure[{$q=$}0.2]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_2.pdf}}
    \subfigure[{$q=$}0.5]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_5.pdf}}
    \subfigure[{$q=$}0.8]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_9.pdf}}
  \\
  \caption{Reputation values of experiments on CIFAR-10 on different imbalance degrees.}
  \label{fig_exp_cifar_reputation}
  \vspace{0.2in}
\end{figure*}

@@

  \subsection{Performance Comparison under Random Attacks}
    From Fig. \ref{fig_exp_extreme}-\ref{fig_table_cifar_random}, we can see that random Byzantine attacks have poor performance against FLPhish-weight and FLPhish-threshold (threshold=0.1, 0.2). We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point like untargeted Byzantine attackers do. While we can see that it has good results in attacking FLPhish-threshold(threshold=0.5) in the CIFAR-10 dataset. From Fig. \ref{fig_exp_cifar_reputation}, we can see that the reputation of benign clients in CIFAR-10 experiments rapidly falls under the threshold of 0.5 due to the complexity of the tasks. With the increase of imbalance degree value $q$, the reputation of the benign clients falls more rapidly in the experiments of the CIFAR-10 dataset than in the experiments of the MNIST and the Fashion-MNIST dataset. As benign clients' reputations in the experiments of the CIFAR-10 dataset become under the threshold $\tau$ of 0.5, they are identified as malicious Byzantine clients as well. As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assit the aggregation, therefore causing a bad performance of FLPhish-threshold (threshold=0.5). While, we can see that FLPhish-threshold (threshold=0.1), FLPhish-threshold (threshold=0.2) and FLPhish-weight stood still against the random Byzantine attacks. The results indicate that the value of the threshold $\tau$ should be considered carefully in the application in some complex tasks.

@@

    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish-threshold and FLPhish-weight under the condition where the Byzantine client portion is a fixed value of 0.5 and distribution imbalance value $q$ is different across the Experiments. The experiment results are shown in Fig. \ref{fig_table_mnist_untargeted}-\ref{fig_table_cifar_untargeted}. We can observe that both the FLPhish-threshold and FLPhish-weight outperform baseline until the imbalance degree $q$ reaches 0.8. The imbalance degree $q$ of 0.8 means that the distribution of data becomes extremely non-IID. The performance of the FLPhish-threshold with a threshold of 0.5 rapidly falls in this case. When facing the distribution of imbalance degree $q=0.8$, each client performs badly, bringing a decline to its reputation. The rise of imbalance degree brings an explosive decline to the global model's accuracy. The accuracy of the global model under the FLPhish-threshold of threshold 0.5 stays 0.1 in the whole learning process. It means that the FLPhish-threshold of threshold 0.5 identifies all the clients as Byzantine clients, making the aggregation process invalid. We can see that the FLPhish-threshold of threshold 0.2 outperforms others. When the distribution becomes non-IID, the threshold of FLPhish-threshold should be set to a lower value to avoid a high false-negative rate. In the experiment of MNIST, it should be set to 0.2. Meanwhile, the performance of FLPhish-weight remains stable under different imbalance degrees.

@@

    \subsubsection{\ul{Performance Comparison with Different Fractions of Byzantine Clients}} Different fractions of Byzantine clients are taken into account as well. Figure. \ref{fig_table_mnist_untargeted}-\ref{fig_table_cifar_untargeted} shows that the accuracy for FedAvg and Ensemble FL without any defense mechanisms begins to fall rapidly when the Byzantine portion reaches nearly 50\%. Furthermore, FedAvg performs extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers. In comparison, FLPhish's (including FLPhish-threshold and FLPhish-weight) performance under various thresholds maintains a high level of performance as the portion grows. Both FLPhish-threshold and FLPhish-weight effectively detect Byzantine clients and accurately discards them from the aggregation process. The global model can be successfully trained without the involvement of Byzantine clients in aggregation procedures. Furthermore, the data show that FLPhish-threshold with a 0.1 threshold performs worse than the other two. This is due to the fact that the 0.1 threshold is far too low to adequately detect Byzantine clients. Though the Byzantine attackers will try to make the right predictions of the public dataset and then send the opposite wrong predictions to the FL server. But they will also make wrong predictions first and coincidentally transfer the opposite right predictions to the FL server. Thus the reputation values of some Byzantine clients, in particular, can exceed 0.1. It indicates that if the threshold is not well set, Byzantine clients can avoid being detected by FLPhish-threshold. As the fractions of Byzantine clients go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks will increase rapidly for they outnumber the fractions of the benign clients. In the meantime, FLPhish-weight shows stable performance whenever the fractions of Byzantine clients are.
